Body size patterns

### 2021-11-16 MS_Analysis_3spp_4rivers_Patterns_from 2spp_bySpp.Rmd
updated figures

vB$speciesGG <- factor(vB$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
vB$seasonGG <- factor(vB$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
vB$riverGG <- factor(vB$riverFactor,
                         levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),
                         labels = c("West Brook","Open Large","Open Small","Isolated Small"))

@@

predGrid2Both$riverGG <- factor(predGrid2Both$riverFactor,
                         levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),
                         labels = c("West Brook","Open Large","Open Small","Isolated Small"))
predGrid2Both$speciesGG <- factor(predGrid2Both$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"))

@@

plotByRiver$speciesGG <- factor(plotByRiver$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
plotByRiver$riverGG <- factor(plotByRiver$riverIndex,
                         levels=c(1,2,3,4),
                         labels = c("West Brook","Open Large","Open Small","Isolated Small"))

>>>>

vB$speciesGG <- factor(vB$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
vB$seasonGG <- factor(vB$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
vB$riverGG <- factor(vB$riverFactor,
                         levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),
                         #labels = c("West Brook","Open Large","Open Small","Isolated Small"))
                         labels = c("West Brook","Open Large","Open Small","Isolated Large"))

@@

predGrid2Both$riverGG <- factor(predGrid2Both$riverFactor,
                         levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),
                         #labels = c("West Brook","Open Large","Open Small","Isolated Small"))
                         labels = c("West Brook","Open Large","Open Small","Isolated Large"))

predGrid2Both$speciesGG <- factor(predGrid2Both$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"))

@@

plotByRiver$speciesGG <- factor(plotByRiver$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
plotByRiver$riverGG <- factor(plotByRiver$riverIndex,
                         levels=c(1,2,3,4),
                         #labels = c("West Brook","Open Large","Open Small","Isolated Small"))
                         labels = c("West Brook","Open Large","Open Small","Isolated Large"))
